Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex
fixed minor stuff
baseline data in
minor changes

We wrote our main control program, classify.py, so that it can choose either
[we're just doing nb and decision trees now right?] classifier and any
combination of  features. On top of this we wrote bash scripts that automated
looping through every combination of classifiers and features, along with
porting the results directly into the scorer.  Classify.py includes a help
switch -h, that explains the switches that control the different classifiers
and features along with any additional parameters that a certain feature might
support (for example, collocation has a window size parameter which defaults to
0) Performance was excellent for most of the features, allowing us to typically
run all of the words in the test set through every combination a classifier and
feature set in under an hour. (The number of runs can get quite high when you
factor in several parameters per feature, not just on/off)

@@

The NLTK was used to implement two machine learning algorithms, naive Bayes and
decision trees.

@@

The NLTK implements a naï bayes classifier which chooses the best sense given a
dictionary of features and assigns confidence probabilities to the chosen
sense. Naive bayes does assume an independence of features. The probability of
each feature contributes to the overall choice.

>>>>

We wrote our main control program, classify.py, so that it can choose either
the Naive Bayes classifier or the Decision Tree classifier and any combination of
features. On top of this we wrote bash scripts that automated
looping through every combination of classifiers and features, along with
porting the results directly into the scorer.  Classify.py includes a help
switch -h, that explains the switches that control the different classifiers
and features along with any additional parameters that a certain feature might
support (for example, collocation has a window size parameter which defaults to
0) Performance was excellent for most of the features, allowing us to typically
run all of the words in the test set through every combination a classifier and
feature set in under an hour. (The number of runs can get quite high when you
factor in several parameters per feature, not just on/off)

@@

The NLTK was used to implement two machine learning algorithms, Naive Bayes and
decision trees.

@@

The NLTK implements a Naive Bayes classifier which chooses the best sense given a
dictionary of features and assigns confidence probabilities to the chosen
sense. Naive Bayes does assume an independence of features. The probability of
each feature contributes to the overall choice.
